### 2021-08-31 CV/cv-sections/honors.tex
CV update
cv update

\begin{cvhonors}

>>>>

\begin{cvhonors}
\cvhonor
{\href{http://federated-learning.org/fl-icml-2021/}{Best Student Paper Award}}
{FL-ICML  2021 Workshop}
{Online}
{2021}

\cvhonor
{\href{https://yandex.ru/scholarships/scholars}{Yandex Ilya Segalovich Scientific Prize}}
{for young researchers}
{Moscow, Russia}
{2021}

\cvhonor
{\href{https://yandex.ru/scholarships/scholars}{Yandex Ilya Segalovich Scientific Prize}}
{for young researchers}
{Moscow, Russia}
{2020}

### 2021-08-31 CV/cv-sections/papers.tex
cv update

@@

\cventry
{Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Alexander Rogozin, Alexander Gasnikov} % Authors
{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} % Title
{\href{https://arxiv.org/abs/2102.09234}{arXiv 2021}} 
{18 Feb 2021} % Date
{}

>>>>

\cventry
{Aleksandr Beznosikov, Alexander Rogozin, Dmitry Kovalev, Alexander Gasnikov} % Authors
{Optimal Decentralized Algorithms for Saddle Point Problems over Time-Varying Networks} % Title
{\href{https://arxiv.org/abs/2107.05957}{arXiv 2021}} 
{13 Jul, 2021} % Date
{}

\cventry
{Dmitry Kovalev, Elnur Gasanov, Peter Richtárik, Alexander Gasnikov} % Authors
{Lower Bounds and Optimal Algorithms for Smooth and Strongly Convex Decentralized Optimization Over Time-Varying Networks} % Title
{\href{http://federated-learning.org/fl-icml-2021/}{ICML 2021 Workshop}} 
{08 Jun 2021} % Date
{}

@@

\cventry
{Dmitry Kovalev, Egor Shulgin, Peter Richtárik, Alexander Rogozin, Alexander Gasnikov} % Authors
{ADOM: Accelerated Decentralized Optimization Method for Time-Varying Networks} % Title
{\href{http://proceedings.mlr.press/v139/kovalev21a}{ICML 2021}} 
{18 Feb 2021} % Date
{}
